Lang-gen model simulations

### 2018-10-11 analysis/model-simulations.Rmd
elephants figure, edits to alternative theories

var x = {asiaStatePosterior, AfricaAndAsiaStatePosterior}
x
'
```

@@

rs.asia <- as.data.frame(rs.eleph$asiaStatePosterior)
rs.asiaafrica <- as.data.frame(rs.eleph$AfricaAndAsiaStatePosterior)

rs.asia.marignals <- bind_rows(
  rs.asia %>%
    rename(state = support.asia) %>%
    group_by(state) %>%
    summarize(prob = sum(probs)) %>%
    mutate(marginal = "asia"),
  rs.asia %>%
    rename(state = support.africa) %>%
    group_by(state) %>%
    summarize(prob = sum(probs)) %>%
    mutate(marginal = "africa")
)

ggplot(rs.asia.marignals, aes(x = state, y = prob))+
  geom_col(position = position_dodge())+
  facet_wrap(~marginal)
```
```{r}
rs.asiaafrica.marignals <- bind_rows(
  rs.asiaafrica %>%
    rename(state = support.asia) %>%
    group_by(state) %>%
    summarize(prob = sum(probs)) %>%
    mutate(marginal = "asia"),
  rs.asiaafrica %>%
    rename(state = support.africa) %>%
    group_by(state) %>%
    summarize(prob = sum(probs)) %>%
    mutate(marginal = "africa")
)

ggplot(rs.asiaafrica.marignals, aes(x = state, y = prob))+
  geom_col(position = position_dodge())+
  facet_wrap(~marginal)
```

>>>>

var x = {asiaStatePosterior, AfricaAndAsiaStatePosterior, statePrior}
x
'
```

@@

rs.asia <- as.data.frame(rs.eleph$asiaStatePosterior)
rs.asiaafrica <- as.data.frame(rs.eleph$AfricaAndAsiaStatePosterior)
rs.asiaafrica.prior <- as.data.frame(rs.eleph$statePrior)

rs.asia.marignals <- bind_rows(
  rs.asia %>%
    rename(state = support.asia) %>%
    group_by(state) %>%
    summarize(prob = sum(probs)) %>%
    mutate(marginal = "africa"),
  rs.asia %>%
    rename(state = support.africa) %>%
    group_by(state) %>%
    summarize(prob = sum(probs)) %>%
    mutate(marginal = "asia")
)

ggplot(rs.asia.marignals, aes(x = state, y = prob))+
  geom_col(position = position_dodge())+
  facet_wrap(~marginal)

rs.asiaafrica.marignals <- bind_rows(
  rs.asiaafrica %>%
    rename(state = support.asia) %>%
    group_by(state) %>%
    summarize(prob = sum(probs)) %>%
    mutate(marginal = "asia"),
  rs.asiaafrica %>%
    rename(state = support.africa) %>%
    group_by(state) %>%
    summarize(prob = sum(probs)) %>%
    mutate(marginal = "africa")
)

ggplot(rs.asiaafrica.marignals, aes(x = state, y = prob))+
  geom_col(position = position_dodge())+
  facet_wrap(~marginal)

rs.asiaafrica.priors <- bind_rows(
  rs.asiaafrica.prior %>%
    rename(state = support.asia) %>%
    group_by(state) %>%
    summarize(prob = sum(probs)) %>%
    mutate(marginal = "asia"),
  rs.asiaafrica.prior %>%
    rename(state = support.africa) %>%
    group_by(state) %>%
    summarize(prob = sum(probs)) %>%
    mutate(marginal = "africa")
)
```

```{r}

save(rs.asia.marignals, rs.asiaafrica.marignals,rs.asiaafrica.priors,
     file = "../paper/cached_results/modelSims-elephants.RData")

fig.eleph.0 <- get_samples(rs.asiaafrica.priors, 10000) %>%
  ggplot(., aes(x = state))+
  geom_density(adjust = 2, fill = 'grey', alpha = 0.3)+
  facet_wrap(~marginal, ncol = 1)+
  ggtitle('prevalence priors')+
  scale_x_continuous(limits = c(0, 1), breaks = c(0, 1))+
  xlab("")+
  ylab("Probability density")

fig.eleph.1 <- get_samples(rs.asia.marignals, 10000) %>%
  ggplot(., aes(x = state))+
  geom_density(adjust = 4, fill = 'grey', alpha = 0.3)+
  facet_wrap(~marginal, ncol = 1)+
  ggtitle('"Elephants live in Africa..."')+
  scale_x_continuous(limits = c(0, 1), breaks = c(0, 1))+
  xlab("Prevalence")+
  ylab("Probability density")+
  theme(axis.title.y = element_blank())

fig.eleph.2 <- get_samples(rs.asiaafrica.marignals, 10000) %>%
  ggplot(., aes(x = state))+
  geom_density(adjust = 4, fill = 'grey', alpha = 0.3)+
  facet_wrap(~marginal, ncol = 1)+
  scale_x_continuous(limits = c(0, 1), breaks = c(0, 1))+
  xlab("")+
  ggtitle('"...and Asia"')+
  ylab("Probability density")+
  theme(axis.title.y = element_blank())

cowplot::plot_grid(
  fig.eleph.0,
  fig.eleph.1,
  fig.eleph.2,
  nrow = 1,
  rel_widths =c(1,1, 1),
  labels = c("A", "B","C")
)
```
